Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-09-02 astronum_2019_MAESTROeX/astronum-maestroex.tex
fixed bibliography entries

All codes in the \amrexastro~suite are open source, with all development carried out in public repositories hosted on GitHub. We believe that having both the codes and the development process completely open promotes good scientific practices, as it means that results from our simulations are reproducible and the codes used to produce them can be investigated.\MarginPar{I feel like there is a better word here than investigated} Others can use the codes for their own scientific investigations, and it is possible to adapt all or parts of the codes to suite new problems. Using version control allows us to keep a record of the codes' development process, helping us to track down bugs and meaning that new and existing developers can learn from previous mistakes. The development branches of the codes are tested nightly using a test suite of problems, checking that any new additions to the code have significantly changed any of the solutions or significantly slowed down the performance.

New versions of the codes are released on the first of each month, and are archived on Zenodo (which also provides us with DOIs, further enhancing the reproducibility of our results).

>>>>

All codes in the \amrexastro~suite are open source, with all development carried out in public repositories hosted on GitHub\footnote{\url{https://github.com/AMReX-Astro}}. We believe that having both the codes and the development process completely open promotes good scientific practices, as it means that results from our simulations are reproducible and the codes used to produce them can be investigated.\MarginPar{I feel like there is a better word here than investigated} Others can use the codes for their own scientific investigations, and it is possible to adapt all or parts of the codes to suite new problems. Using version control allows us to keep a record of the codes' development process, helping us to track down bugs and meaning that new and existing developers can learn from previous mistakes. The development branches of the codes are tested nightly using a test suite of problems, checking that any new additions to the code have significantly changed any of the solutions or significantly slowed down the performance.

New versions of the codes are released on the first of each month, and are archived on Zenodo\footnote{\url{https://zenodo.org/}} (which also provides us with DOIs, further enhancing the reproducibility of our results).
